\documentclass[a4paper,10pt]{article}
\usepackage{graphicx}
\usepackage{float}
\usepackage{multirow}
\usepackage[left=0.75in,right=0.75in,top=0.75in,bottom=0.75in]{geometry}
\usepackage{fontspec}
\usepackage{textcomp}
\usepackage{setspace}
\newcommand{\header}[1]{
\begin{center}
\fbox{\begin{minipage}{\textwidth}
\raggedright \large \bf #1
\end{minipage}}
\end{center}
\vspace{-0.3cm}
}
\pagestyle{empty}
\begin{document}
\setmainfont{Ubuntu}
\begingroup
\setlength{\tabcolsep}{0.05\textwidth}
\begin{table}[h!]
 \centering
 \begin{tabular}{p{0.5\textwidth} p{0.5\textwidth}}
 \hspace{-0.6cm}\bf Sushant Mahajan & \hspace{0.5cm}\bf Computer Science \& Engineering \\
 & \hspace{0.5cm}\bf MTech, IIT Bombay \\
 \hspace{-0.6cm}\textbf{Email:} sushant.mahajan88@gmail.com & \\
 \hspace{-0.6cm}\textbf{Phone:} 7506112001 & \\ 
 \end{tabular}
\end{table}
\endgroup
\vspace*{-1cm}
\header{Academic details}
\vspace*{-0.2cm}
\begin{table}[h!]
  \centering
  \begin{tabular}{l l l l l}
  \hspace*{-0.22cm}\bf Examination & \bf University & \bf Institute & \bf Year & \bf CPI/\% \\
  \hspace*{-0.22cm}Post Graduation & IIT Bombay & IIT Bombay & 2016 & 9.05 \\
  \hspace*{-0.22cm}Undergraduate Specialization: CSE & & & & \\
  \hspace*{-0.22cm}Graduation & JIIT, Noida & Jaypee Institute of Information Technlogy & 2011 & 7.7 \\
  \hspace*{-0.22cm}Intermediate/+2 & CISCE & St. Joseph's Academy, Dehradun & 2006 & 92.5\% \\
  \hspace*{-0.22cm}Matriculation & CISCE & St. Joseph's Academy, Dehradun & 2004 & 89\% \\
  \end{tabular}
\end{table}

% \vspace*{2.4in}
 \vspace{-0.8cm}
\header{Awards and Achievements}
\vspace{-0.2cm}
\begin{itemize}
 \item Secured percentile of \textbf{99.81 amongst 224160} students in \textbf{GATE 2013}.
 \item Participated in \textbf{Microsoft code.fun.do}, 2016.
 \item Ranked \textbf{6\textsuperscript{th} of 2500} candidates in HP Hack-a-thon, Hackerearth 2015.
 \item Part of team to reach \textbf{semi-finals} in Hackerrank Worldcup, 2015.
 \item \textbf{Oracle\textregistered ~Certified Professional} JAVA SE 6 Programmer. Cleared OCP-JP 6, 2014 with 90\%.
 \item \textbf{Microsoft\textregistered ~Specialist} in programming in HTML5 with JavaScript and CSS3, 2012. Cleared the certification with 76\%.
 \item Ranked \textbf{6\textsuperscript{th} of 200} students in college's annual computer science conference \textbf{IC3, 2010} for the project \textbf{Voice controlled obstacle detector}.
 \item \textbf{1\textsuperscript{st} in Debugging/C++} programming contest in college's annual fest \textbf{JIVE, 2009}.
\end{itemize}

\vspace{-0.8cm}
\header{Fields of Interest}
\vspace{0.2cm}
Cryptography, Cloud computing, Software Architecture, Machine Learning

\vspace{-0.4cm}
\header{Industry Experience - 24 months}
\vspace{0.2cm}
\noindent{Worked as \textbf{ASE at CSC India Pvt. Ltd., Noida}. My project was in Healthcare domain, in a team of 13. The software is used by clinicians at hospitals in Denmark, where healthcare is mostly public. Objective is to document and co-ordinate all activities related to treatment of a patient. I worked on 4 modules.
\begin{itemize}
 \item \textbf{Module 1:} Enables \textbf{creation, saving and editing of RTF text} in admin application and provide the API for the usage of the text in the main client module. \\
 \textbf{Responsibilities:} Technical design, implementation, testing.
 
 \item \textbf{Module 2:} Did work relating to extendability of the module by changing the core design patterns. \\
 \textbf{Responsibilities:} Technical design, POC for design patterns, implementation, testing.
 
 \item \textbf{Module 3:} Extended list based design to include working with multiple items. Extension of module 2. \\
 \textbf{Responsibilities:} Implementation, testing.
 
 \item \textbf{Module 4-Internal:} Aimed at reducing the time required for preparing a new Environment to run the application and JUnit test cases on it, from a few days to a few hours. It helps a developer/tester to load appropriate data required into the DB. It can be compared to a class loader in JAVA. \\
 \textbf{Responsibilities:} Create user stories, Analysis of codes, implementation, review, documentation, testing.
\end{itemize}
\textbf{Technologies/Tools:} JAVA SE-6(Core), Swing, XML, Oracle, HTB DB Framework, Design Patterns, SONAR Quality tool, UISpec4J UI testing tool, QAPlug source code quality, SVN.
}

\vspace{-0.4cm}
\header{MTech Courses}
\begin{table}[H]
 \begin{tabular}{p{0.5\textwidth} p{0.5\textwidth}}
  Program Analysis & Network Security and Cryptography II\\
  Natural Language Processing & Software  Architecture\\
  Computer Networks & Design and Implementation of GCC Framework\\
  Engineering a Cloud & Number Theory and Cryptography
 \end{tabular}
\end{table}

\vspace{-0.4cm}
\header{Post Graduate Research/Projects}
\vspace{0.2cm}
\begingroup
\linespread{0.5}
\textbf{Homomorphic Encryption Over Vectors with application to SCM -} \emph{M.Tech. Thesis}\hfill[Autumn 2015 - present] \\
\emph{Guide: Prof. Bernard Menezes}
\begin{itemize}
 \item Goal: Implement Zhou's scheme for efficient homomorphic encryption over 
integer vectors and improve performance by making use of multiple cores and multiprocessing.\\
Apply the above solution to predict inventory needs based past data which would be homomorphically encrypted.
\end{itemize}

\noindent
\textbf{Homomorphic Cryptography -} \emph{M.Tech. Seminar}\hfill[Spring 2014] \\
\emph{Guide: Prof. Bernard Menezes}
\begin{itemize}
 \item Goal: Survey various techniques that allow homomorphic encryption of data fully or partially. The relative efficacy of the techniques and the practicality of the implementation was also researched.
\end{itemize}

\noindent
\textbf{Cloud based memcache clone -} \emph{Course Project}\hfill[Spring 2014] \\
\emph{Guide: Prof. Sriram Srinivasan}
\begin{itemize}
 \item Goal: The memcache supports basic atomic instructions like set, get, cas for key value pairs. 5 servers maintain a replicated memcache table. The servers are cemented together with a RAFT based consensus algorithm.
 \item Technologies/Tools: Google go, git, lite IDE
\end{itemize}

\noindent
\textbf{Emotion detection from live chat -} \emph{Course Project}\hfill[Autumn 2014] \\
\emph{Guide: Prof. Pushpak Bhattacharyya}
\begin{itemize}
 \item Goal: Develop a system to analyze data from a text based chat, and as an output display the predicted emotion portrayed. We developed 3 models comprising chained application of prediction algorithms - naive bayes, linear svc and multinomial naive bayes with TF-IDF and Chi$^2$ selection; Vector space models; frequency based prediction and analyzed the results. We also built the chat server-client application.
 \item Technologies/Tools: Python3, Tkinter, bash, nltk, wordnet
\end{itemize}

\noindent
\textbf{QT based SpecRTL  visualizer -} \emph{Course Project}\hfill[Spring 2013] \\
\emph{Guide: Prof. Uday Khedkar}
\begin{itemize}
 \item Goal: SpecRTL is a language for machine descriptions. Although easy to write it is very difficult to visualize the structures. We wrote a Qt based tool which takes as input the specRTL code and produces a tree based graphic output.
 \item Technologies/Tools: C/C++, Qt developer kit, specRTL
\end{itemize}
\endgroup

\vspace{-0.8cm}
\header{RA Work - System Administrator}
\vspace{-0.2cm}
\begin{itemize}
 \item Wrote scripts for automatic software installation, iptables manipulation and regular lab maintenance.
 \item Established the FOG server for automated creation and deployment of OS images on all lab systems, greatly reducing the man hours required.
 \item Deployed printer bank and wrote the web interface for printing documents using the department printers.
 \item Wrote scripts and programs for creating a printer accounting solution.
 \item Deployed iSCSI based filesystem that is used by all lab machines via NFS.
 \item Configured department servers with IPMI for low level management and emergency maintenance.
\end{itemize}

\vspace{-0.8cm}
\header{Skills}
\vspace{0.1cm}
\begin{itemize}
 \item \textbf{Languages:} C/C++, JAVA 6(Core), Google Go, Python, bash
 \item \textbf{OS:} GNU/Linux (Ubuntu, Debian)
 \item \textbf{Web technologies:} HTML5, CSS3, JavaScript, PHP, JSP, Servlets, Bootstrap, JSON
 \item \textbf{Tools:} gnuplot, \LaTeX, git, vim, Eclipse
 \item \textbf{Database:} MySql
\end{itemize}
\end{document}
